slides for lab

### 2023-09-06 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Limited join to just person_id
Updates for the abstract

```{r cohort dates}
date_cohort_month_start <- ymd(params$date_cohort_month)
date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
```

@@

>>>>

```{r cohort dates}
date_cohort_month_start <- ymd(params$date_cohort_month)
date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
date_observation_window_month_end <- 
  # ceiling_date(date_observation_window_month_start,unit = "month") %>% 
  date_observation_window_month_start %>% 
  rollbackward()
```

@@

```{r}
prep_building <- 
  prep_building %>% 
  left_join(prep_xx, by = "person_id")
```

### 2023-09-06 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Updates for the abstract

---
title: "Data analysis for employee cluster descriptive statistics"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-08-09.rdata"
  data_file_2: "prep_employees_2023-08-09.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"

@@

>>>>

---
title: "Data analysis for employee cluster descriptive statistics"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-09-06.rdata"
  data_file_2: "prep_employees_2023-09-06.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"

@@

```{r}
d %>% count(duty_station_code)
```

### 2023-09-06 04. Analysis/scripts/04-01-reporting-presentation.Rmd
Updates for the abstract

---
title: "slides for lab"
author: "Ben Jaques-Leslie"
date: "2023-08-22"
output: powerpoint_presentation
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-08-09.rdata"
  data_file_2: "prep_employees_2023-08-09.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"
---

@@

```{r include=FALSE}
d <- d %>% 
  mutate(
    .cluster_5 = fct_recode(.cluster_5,
                            "Teleworkers" = "1",
                            "Office visitors" = "2",
                            "Hybrid workers" = "3",
                            "In-office workers" = "4",
                            "Disconnected workers" = "5"),
    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
  )
```

@@

1.  Teleworkers

@@

# Teleworkers, office visitors, and regions

@@

prep_d_04 <- 
  prep_d_03 %>% 
  filter(.cluster_5 == "Teleworkers" |
           .cluster_5 == "Office\nvisitors"
           )
```

@@

-   Teleworkers and office visitors are very common for those that live in states neighboring DC

>>>>

---
title: "slides for lab"
author: "Ben Jaques-Leslie"
date: "2023-08-22"
output: powerpoint_presentation
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-09-06.rdata"
  data_file_2: "prep_employees_2023-09-06.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"
---

@@

```{r include=FALSE}
d <- d %>% 
  mutate(
    .cluster_5 = fct_recode(.cluster_5,
                            "Telecommuters" = "1",
                            "Office visitors" = "2",
                            "Hybrid workers" = "3",
                            "In-office workers" = "4",
                            "Disconnected workers" = "5"),
    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
  )
```

@@

1.  Telecommuters

@@

# Telecommuters, office visitors, and regions

@@

prep_d_04 <- 
  prep_d_03 %>% 
  filter(.cluster_5 == "Telecommuters" |
           .cluster_5 == "Office\nvisitors"
           )
```

@@

-   Telecommuters and office visitors are very common for those that live in states neighboring DC
